\chapter{The \cls{MRTthesis} class}
\cls{MRTthesis} provides the template to write a thesis at the MRT. It sports a
layout which looks confusingly similar to the MS Word template provided by the
chair. Of course there are some minor differences and the typesetting algorithm
of TeX should create better line breaking than Word's but if one doesn't know on
what to pay attention or for an untrained eye the distinction won't be possible
(at least I hope so, as that was the goal in the first place).

\section{Options}%>>>
\subsection{Load time options}\label{sec:thesis:opt}%>>>
The class features a few load time options, none of which do take arguments.
\begin{describeopt}{longtable}
  Is forwarded to \pkg{MRTtab} see its description in \autoref{sec:tab:options}.
\end{describeopt}
\begin{describeopt}{hidelinks}
  If used the \pkg{hyperref} option of the same name will be used. By default
  this is used. You can negate it with \opt{showlinks}.
\end{describeopt}
\begin{describeopt}{mathsizes}
  Opposite of \opt{no mathsizes}. If used (which it by default is) the maths
  sizes are set according to the MS Word template. Note that those weren't set
  by \pkg{mrtarbeit} and if you alter the default font size won't be set.
\end{describeopt}
\begin{describeopt}{minimal}
  If this option is passed some packages are not loaded and therefore related
  configurations not set. See \autoref{sec:thesis:dep}.
\end{describeopt}
\begin{describeopt}{no geometry}
  If this option is passed the \pkg{geometry} package is not loaded (and of
  course the page dimensions passed to \pkg{geometry} otherwise are not set).
\end{describeopt}
\begin{describeopt}{no mathsizes}
  Opposite of \opt{mathsizes}. If used the maths sizes are not changed from the
  defaults of \cls{scrreprt}.
\end{describeopt}
\begin{describeopt}{showlinks}
  If used the \pkg{hyperref} option \verb|hidelinks| will not be used. This is
  the negation of \opt{hidelinks} of this package.
\end{describeopt}
\begin{describeopt}{tikzunderline, tUline}
  This option is forwarded to \pkg{MRTwuline}.
\end{describeopt}
\begin{describeopt}{british,english,UKenglish}
  If used the document will be using the \opt{british} definition of
  \pkg{babel}. Many strings used in the package will be in English, but some
  might be missed out. If you find any of which you think should be translated,
  please contact me as described in \autoref{sec:bugs}. English simplified (US)
  is not supported by the class.
\end{describeopt}

\noindent
Every other given option will be passed on to \cls{scrreprt}.
%<<<
\subsection{Setup options}\label{sec:thesis:setup}%>>>
The following options are accessible with \cs{MRTthesisSetup}.
\begin{describeopt}{advisor}[\meta{name}]
  Sets the name of the advisor of this thesis. One typical value could be
  \texttt{Dipl.-Ing.\@ Alice Fischerauer}
\end{describeopt}
\begin{describeopt}{author}[\meta{name}]
  Sets the name of the author or authors as the macro \cs{author} does.
  Separate authors with \cs{and}. You can give the surname first followed by a
  comma and the given name, in which case the parsing for the abbreviation works
  better (especially with name affixes). The following two options are fine:
  \texttt{author=\{Duck, Donald \string\and\ Mouse, Mickey\}} or
  \texttt{author=\{Donald Duck \string\and\ Mickey Mouse\}} and should both
  result in the abbreviation \texttt{D.\@ Duck, M.\@ Mouse}. Another example
  would be \texttt{zu Guttenberg, Karl-Theodor} or \texttt{Karl-Theodor zu
  Guttenberg}. Here the parsing would result in \texttt{K.-T.\@ zu Guttenberg}
  or \texttt{K.-T.\@ z.\@ Guttenberg} -- the first one seems correct, the second
  one fails. Remember to surround the argument with braces if you use a comma.
\end{describeopt}
\begin{describeopt}{caption above}
  Is forwarded to \pkg{MRTtab}. See \autoref{sec:tab:options:setup}.
\end{describeopt}
\begin{describeopt}{caption below}
  Is forwarded to \pkg{MRTtab}. See \autoref{sec:tab:options:setup}.
\end{describeopt}
\begin{describeopt}{citation width}[\meta{dimen}]
  The width of the citation indications on the title page. Default is
  \verb|.5\textwidth|.
\end{describeopt}
\begin{describeopt}{degree}[\meta{degree}]
  The degree you aim to achieve with the thesis. If you don't use this option it
  is tried to be guessed from the type of thesis you can specify with the
  \opt{thesis} key. An error is thrown if the degree can't be guessed. If you
  don't want to achieve any degree, use the option \opt{no degree}. Typical
  values would be \verb|Bachelor of Science| or \verb|Master of Science|.
\end{describeopt}
\begin{describeopt}{examiner}[\meta{name}]
  The examiner of the thesis. Initial value is
  \texttt{Univ.-Professor Dr.-Ing.}\hskip0pt\ \texttt{Gerhard Fischerauer}.
\end{describeopt}
\begin{describeopt}{logoL}[\meta{file}]
  The image file for the left logo on the titlepage. Initial value is
  \file{MRTthesis_logo_UBT2.pdf}. If \meta{file} is an empty argument no left
  logo will be used.
\end{describeopt}
\begin{describeopt}{logoL height}[\meta{dimen}]
  The height the left logo is displayed in. Initial value is \verb|10.85mm|.
\end{describeopt}
\begin{describeopt}{logoR}[\meta{file}]
  The image file for the right logo on the titlepage. Initial value is
  \file{MRTthesis_logo_MRT2.pdf}. If \meta{file} is an empty argument no right
  logo will be used.
\end{describeopt}
\begin{describeopt}{logoR height}[\meta{dimen}]
  The height the right logo is displayed in. Initial value is \verb|11.9mm|.
\end{describeopt}
\begin{describeopt}{no advisor}[\meta{bool}]
  If true no advisor will be displayed on the title page. Default is true,
  initially is false.
\end{describeopt}
\begin{describeopt}{no citation}[\meta{bool}]
  If true no citation indications are displayed at the bottom of the title page.
  Default is true, initially is false.
\end{describeopt}
\begin{describeopt}{no degree}[\meta{bool}]
  If true no degree will be displayed on the title page. Default is true,
  initially is false. Also the paragraph corresponding to the degree in the
  affidavit will be left out.
\end{describeopt}
\begin{describeopt}{no examiner}[\meta{bool}]
  If true no examiner will be displayed on the title page. Default is true,
  initially is false.
\end{describeopt}
\begin{describeopt}{no chair}[\meta{bool}]
  If true no chair will be displayed on the title page. Default is true,
  initially is false.
\end{describeopt}
\begin{describeopt}{no logos}
  If used \verb|logoL={},logoR={}| is used, which results in no logos on the
  title page.
\end{describeopt}
\begin{describeopt}{no thesis}[\meta{bool}]
  If true no thesis type will be displayed on the title page. Default is true,
  initially is false.
\end{describeopt}
\begin{describeopt}{no usage}[\meta{bool}]
  If true no usage rights are given to the MRT in the affidavit text. Default is
  true, initially is false. If you need a custom paragraph and don't want to
  leave it out completely you should redefine \cs{affidavittext@usagerights}.
\end{describeopt}
\begin{describeopt}{number}[\meta{number}]
  The MRT report number displayed in the citation indications. Initially is
  empty. The typical pattern of these numbers is something like:
  \texttt{TT-yy-mm-n} with \texttt{TT} the thesis type, e.\,g.\@ \texttt{BA} or
  \texttt{MA}, \texttt{yy} the last two digits of the year, \texttt{mm} the
  month, and \texttt{n} the number of the thesis in this month.
\end{describeopt}
\begin{describeopt}{pos figure}[\meta{placement}]
  The \meta{placement} of floats of type \texttt{figure}.
\end{describeopt}
\begin{describeopt}{pos float}[\meta{placement}]
  The \meta{placement} of floats of both types, \texttt{figure} and
  \texttt{table}. Initially set to \texttt{tbp}.
\end{describeopt}
\begin{describeopt}{pos MRTtable}[\meta{placement}]
  The \meta{placement} of floating \env{MRTtable}s, forwarded to \pkg{MRTtab}'s
  option \opt{pos}. See \autoref{sec:tab:options:setup}.
\end{describeopt}
\begin{describeopt}{pos table}[\meta{placement}]
  The \meta{placement} of floats of type \texttt{table}.
\end{describeopt}
\begin{describeopt}{short advisor, sadvisor}[\meta{abbreviation}]
  The abbreviated name of the advisor. This is needed for the citation
  indications and not parsed automatically from the \opt{advisor}, as the name
  contains academic titles, but the abbreviation should not and the parsing
  would be hard to do correctly.
\end{describeopt}
\begin{describeopt}{short author, sauthor}[\meta{abbreviation}]
  The abbreviated name or names of the author or authors. If you don't use this
  option it is tried to parse those automatically. If the parsing does something
  wrong you'll have to use this option giving the correct abbreviations with
  each name separated with commas from the others, e.\,g.\@ 
  \texttt{short author=\{D. Duck, M. Mouse\}}.
\end{describeopt}
\begin{describeopt}{short examiner, sexaminer}[\meta{abbreviation}]
  The abbreviated name of the examiner. This is needed for the citation
  indications and not parsed automatically from the \opt{examiner}, as the name
  contains academic titles, but the abbreviation should not and parsing would be
  hard to do correctly. Initially value is \texttt{G.\@ Fischerauer}.
\end{describeopt}
\begin{describeopt}{sign height}[\meta{dimen}]
  The height reserved for each signature below the affidavit text. Initial value
  is \texttt{9mm}.
\end{describeopt}
\begin{describeopt}{sign separation, sign sep}[\meta{dimen}]
  If \opt{sign width max} is not given (or \texttt{0pt}) the maximum width is
  calculated from the text width and the width of the date and location. The
  minimum distance from the date and location to the signature lines is then
  enforced to be at least \meta{dimen}. Initial value is \texttt{2em}.
\end{describeopt}
\begin{describeopt}{sign width max}[\meta{dimen}]
  You can enforce a maximum width for the signature lines below the affidavit
  using this option. If it is not used, the maximum width is calculated.
\end{describeopt}
\begin{describeopt}{sign width min}[\meta{dimen}]
  You can enforce a minimum width for the signature lines using this option.
  Initially this is set to \texttt{7cm}.
\end{describeopt}
\begin{describeopt}{stretch caption, stretch cap}[\meta{float}]
  Uses \cs{setkomafont} to enforce a specific line spread using \cs{setstretch}
  for captions.
\end{describeopt}
\begin{describeopt}{stretch tabular, stretch tab}[\meta{float}]
  Is forwarded to \pkg{MRTtab}'s option \opt{stretch tab}. See
  \autoref{sec:tab:options:setup}.
\end{describeopt}
\begin{describeopt}{stretch text}[\meta{float}]
  Uses \cs{setstretch} to set a specific line spread in the document.
\end{describeopt}
\begin{describeopt}{stretches}[\meta{float}]
  Sets \opt{stretch cap}, \opt{stretch tab}, and \opt{stretch text} in one go.
  Initially set to \texttt{1.408}.
\end{describeopt}
\begin{describeopt}{subtitle}[\meta{title}]
  The title page might include a subtitle. If you really want to use it, you'd
  have to use \opt{with subtitle}. You can also use \cs{subtitle} to set it.
\end{describeopt}
\begin{describeopt}{thesis}[\meta{thesis type}]
  Sets the \meta{thesis type}. Typical arguments would be
  \texttt{Bachelorarbeit} or \texttt{Bachelor Thesis} (the former if you're
  writing in German, the latter if you're writing in English).
\end{describeopt}
\begin{describeopt}{title}[\meta{title}]
  Sets the title of the thesis. You might also use \cs{title} to set this.
\end{describeopt}
\begin{describeopt}{toc ChapIndent}[\meta{dimen}]
  Sets the indentation of chapter entries in the table of contents. Initially
  set to \texttt{0.01em}.
\end{describeopt}
\begin{describeopt}{toc SecIndent}[\meta{dimen}]
  Sets the indentation of section entries in the table of contents. Initially
  set to \texttt{1.32em}. The width is also used for entries in the list of
  figures and list of tables.
\end{describeopt}
\begin{describeopt}{toc sSecIndent}[\meta{dimen}]
  Sets the indentation of subsection entries in the table of contents. Initially
  set to \texttt{3.38em}.
\end{describeopt}
\begin{describeopt}{toc ssSecIndent}[\meta{dimen}]
  Sets the indentation of subsubsection entries in the table of contents.
  Initially set to \texttt{6.38em}.
\end{describeopt}
\begin{describeopt}{with subtitle}[\meta{bool}]
  If true a subtitle can be used on the title page. Default is true, initially
  is false.
\end{describeopt}
%<<<
%<<<

\section{Macros}\label{sec:thesis:mac}%>>>
The following macros are provided:
\begin{describemacroTF}{ifNoWidth}[\marg{arg}]
  Typesets the argument in a box (so the code is actually executed). If the
  produced box has a width of 0pt the \meta{true} branch is executed, else the
  \meta{false} branch.
\end{describemacroTF}
\begin{describemacro}{vfillmult}[\marg{num}]
  Same as if you'd use \meta{num} instances of \cs{vfill}.
\end{describemacro}
\begin{describemacro}{hfillmult}[\marg{num}]
  Same as if you'd use \meta{num} instances of \cs{hfill}.
\end{describemacro}
\begin{describemacro}{MRTafterhyperref}[\marg{content}]
  Places \meta{content} after \pkg{hyperref} is loaded. This is important for
  the relative few packages that need to be loaded after \pkg{hyperref}. So if
  you have one of these, you should use something like
  \verb|\MRTafterhyperref|\hskip0pt
  \verb|{\usepackage|\hskip0pt
  \verb|{cleveref}}|. This macro has to be used prior to
  \verb|\begin|\hskip0pt
  \verb|{document}|.
\end{describemacro}
\begin{describemacro}{DeclareTOCStyleEntryMRTChapterLike}%
  [\oarg{indent}\hskip0pt\marg{entry-layer}]
  See the description of \cs{DeclareTOCStyleEntryMRTSectionLike}. The difference
  is that this sets the entries how the chapters are formatted. Also the
  \meta{indent} defaults to the one of chapters.
\end{describemacro}
\begin{describemacro}{DeclareTOCStyleEntryMRTSectionLike}%
  [\oarg{indent}\hskip0pt\marg{entry-layer}]
  The macro calls the KOMA macro \cs{DeclareTOCStyleEntry} and sets the options
  how they are used for the section entries in the table of contents.
  \meta{indent} defaults to the indent length of section entries. It is possible
  to use an \meta{indent} but give more options in that optional argument
  afterwards (comma separated). \autoref{tab:thesis:tocindents} shows an
  overview of the class's default indentations.
\end{describemacro}
\begin{MRTtable}%>>>
  [%>>>
    ,label=tab:thesis:tocindents
    ,cap=
      {
        Indents of different ToC entry types and the macros they are stored in.
        Use the options described in \autoref{sec:thesis:setup} to change the
        values.
      }
    ,scap=
      {Indents of different ToC entry types and the macro they are stored in}
    ,col=llc
  ]%<<<
  entry-layer & macro name & default length \\

  chapter       & \cs{l_MRTthesis_toc_chapter_indent_tl}       & 0.01em\\
  section       & \cs{l_MRTthesis_toc_section_indent_tl}       & 1.32em\\
  subsection    & \cs{l_MRTthesis_toc_subsection_indent_tl}    & 3.38em\\
  subsubsection & \cs{l_MRTthesis_toc_subsubsection_indent_tl} & 6.38em\\
  table         & \cs{l_MRTthesis_toc_section_indent_tl}       & 1.32em\\
  figure        & \cs{l_MRTthesis_toc_section_indent_tl}       & 1.32em\\
\end{MRTtable}%<<<
\begin{describemacro}{MRTthesisSetup}[\marg{options}]
  You can use this macro to set the options listed in
  \autoref{sec:thesis:setup}.
\end{describemacro}
\begin{describemacro}{sethead}[\marg{content}]
  Sets the head marks for both sides to \meta{content}. It is the same as
  \cs{markboth}\hskip0pt
  \texttt{\{\meta{content}\}\hskip0pt\{\meta{content}\}}. You might use this (or
  any similar macro provided by KOMA script) to manually set the head marks,
  e.\,g.\@ if your section title gets too long.
\end{describemacro}
\begin{describemacro}{affidavit}
  Prints a chapter ``Eidesstattliche Erklärung'' and the affidavit text (as
  stored in \cs{affidavit@text}) and the location and date, followed by a
  signature line for each author. \cs{maketitle} has to be used prior to it,
  else the lines won't be printed. This is a bug I might fix in the future.
\end{describemacro}
\begin{describemacro}{mainpart,mainmatter}
  Switches the formatting from the one at the beginning to the one used in the
  main part of the document. Should be used after \cs{tableofcontents},
  \cs{listoffigures}, and \cs{listoftables}.
\end{describemacro}
\begin{describemacro}{appendix}
  Switches the formatting to the one used in the appendix. This includes
  switching to alphabetically numbered sections and setting the option \opt{no
  float} in \cs{MRTtabSetup}.
\end{describemacro}
Additionally the macros \cs{author}, \cs{title}, and \cs{subtitle} have been
redefined to internally use \cs{MRTthesisSetup} to set the corresponding
options.
%<<<

\section{Dependencies}\label{sec:thesis:dep}%>>>
As this class is based on \cls{scrreprt}, it depends on that class and all of
its dependencies, of course. Additionally the following packages are loaded
(used options given in brackets). Those are quite some but unfortunately most of
these are required (or help a lot) to achieve certain formattings in order to
match the MS Word template of the MRT best.

Some of the used packages are not necessarily needed to match the MS Word
template, but provide useful features -- e.g.  \pkg{hyperref} which allows the
use of \cs{autoref} and cross linking but is not needed to match any specific
formatting.%
\footnote
  {Don't remove it though, the current code for section headings relies on it.}

\begin{multicols}{2}%>>>
  \begin{itemize}[leftmargin=10pt]
    \item \pkg{expl3}
    \item \pkg{xparse}
    \item \pkg{MRTif}
    \item \pkg{MRTsfacc}
    \item \pkg{MRTtab}
    \item \pkg{MRTwuline}
    \item If \hologo{XeTeX} or \hologo{LuaTeX} are used
      \begin{itemize}[topsep=0pt]
        \item \pkg{fontspec} and
          \verb|\defaultfontfeatures|\hskip0pt\verb|{Ligatures=TeX}|
      \end{itemize}
      else
      \begin{itemize}[topsep=0pt]
        \item \pkg{fontenc} [T1]
        \item \pkg{inputenc} [utf8]
      \end{itemize}
    \item \pkg{lmodern}
    \item \pkg{helvet}
    \item \pkg{babel} [ngerman] or if \opt{british} is used with
      [main=british, ngerman]
    \item \pkg{scrlayer-scrpage} [singlespacing=true]
    \item \pkg{geometry} (with correct options)
    \item \pkg{setspace}
    \item \pkg{xcolor}
    \item \pkg{graphicx}
    \item \pkg{enumitem}
    \item \pkg{mathtools}
    \item \pkg{mathastext} [italic,defaultmathsizes]
    \item \pkg{isomath}
    \item \pkg{hyperref}
    \item if the \opt{minimal} option is not used:
      \begin{itemize}
        \item \pkg{siunitx}
          [%
            detect-all,
            per-mode=reciprocal-positive-first%
          ]\\
          If \pkg{babel}'s \opt{british} is used [locale=UK] will be used, if
          \opt{ngerman} [locale=DE]. Additionally the \opt{range-phrase} will be
          set to either \texttt{to} or \texttt{bis} with spaces around it.
        \item \pkg{biblatex}
          [%
            backend=biber, natbib=true, citestyle=numeric, bibstyle=numeric,
            sorting=none, giveninits=true, sortcites%
          ] (with URLs being line breakable at any place)
        \item \pkg{csquotes}
      \end{itemize}
  \end{itemize}
\end{multicols}%<<<
%<<<
